---
title       : Reproducible Pitch
subtitle    : Course Project
author      : Bernd Meyer
job         : 
framework   : shower        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {selfcontained, standalone, draft}
knit        : slidify::knit2slides
---

## Reproducible Pitch
### Bernd Meyer
#### May 6 2020

---

## My Shiny App 

- My app "Adding and Deleting Points" fits a linear model mpg ~ wt for the mtcars dataset.
- It allows the user to delete and add points in the scatter plot.
- Each point a represents an observation. Deleted points are excluded from the model data.
- The coefficients for the linear model are being updated after any changes to the points.

---
## Model

- The model is lm(mpg ~ wt, data = mtcars)
- Below are the models coefficients with the full mtcars dataset. 
```{r}
summary(lm(mpg ~ wt, data = mtcars))$coef
```

---

## Plot Code

```{r eval=FALSE}
library(ggplot2)
ggplot(mtcars, aes(wt, mpg)) + geom_point() +
    geom_smooth(method = lm, 
                fullrange = TRUE, color = "black") +
    geom_point() + ggtitle("mtcars: lm(mpg ~ wt)") +
    coord_cartesian(xlim = c(1.5, 5.5), ylim = c(5,35))

```

---

## Plot 

```{r pressure, fig.height=4.5, fig.width=8, echo=FALSE, message=FALSE}
ggplot(mtcars, aes(wt, mpg)) + geom_point() +
    geom_smooth(method = lm, 
                fullrange = TRUE, color = "black") +
    geom_point() + ggtitle("mtcars: lm(mpg ~ wt)") +
    coord_cartesian(xlim = c(1.5, 5.5), ylim = c(5,35))
```





